The Effect of Weather Shocks on Children's Education in Bolivia

### 2020-05-10 final_seminar_paper.Rmd
where the r document is at right now...won't read again

#The following custom function simplifies the process of writing dfSummaries to html files
export_summary_table <- function(dfSummary_output){
  data_info <- attr(dfSummary_output, "data_info")
  ds_name <- data_info$Data.frame
  print(dfSummary_output,
      file = str_c("output/", ds_name, "_summary.html"),
      method = "browser",
      report.title = ds_name)
}
```
# Introduction

@@

>>>>

#The following custom function simplifies the process of writing dfSummaries to html files
export_summary_table <- function(dfSummary_output){
  data_info <- attr(dfSummary_output, "data_info")
  ds_name <- data_info$Data.frame
  print(dfSummary_output,
      file = str_c("output/", ds_name, "_summary.html"),
      method = "browser",
      report.title = ds_name)
}
```

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

# Introduction

@@

```{r probit regression rural sample extr, echo = F, warning = F, message = F}

probitMod_assist_rx <- glm(attend ~ floods + flood_secondary + flood_pov + droughts + drought_secondary + drought_pov + age + female + extr + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural, family=binomial(link="probit"))

probitMod_register_rx <- glm(register ~ floods + flood_pov + droughts + drought_pov + age + female + extr + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural, family=binomial(link="probit"))

probitMod_work_rx <- glm(work_reason ~ floods + flood_secondary + flood_pov + droughts + drought_secondary + drought_pov + age + female + extr + secondary + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural, family=binomial(link="probit"))

```{r generate probit regression table rural sample extr, echo = F, results = "asis"}
stargazer::stargazer(list(probitMod_assist_rx, probitMod_register_rx, probitMod_work_rx), 
               title = "Rural sample probit regression results (poverty measure)", 
               label = "fullResults9",
               header = F,
               keep = c("floods", "droughts", "flood_secondary", "drought_secondary", "flood_pov", "drought_pov","age", "female", "extr", "secondary", "child", "grandchild", "num_children", "hhhead_educ", "female_hhhead"))
